A linearization procedure for constrained multibody systems

### 2012-09-29 PetersonGedeHubbard2012.tex
Revised abstract.

\begin{abstract}
% Context
Many common mechanical systems have configuration or velocity constraints.
% Need  (what we have and what we want)
Analyses of such systems often require linearized forms of the motion
equations.  The derivation of the nonlinear motion equations is well
understood, but very little has been presented on the proper approach to
forming linearized versions which satisfy the constraints.
% Task
To address this issue, we formed a procedure of organizing the constraints
and motion equations, and subsequently linearizing these equations.
% Object of the document
In this paper we present this procedure to correctly linearize the nonlinear
motion equations of constrained multibody systems, and illustrate it with a
familiar example.
% Findings
We applied this procedure to a model of a bicycle which includes a closed
kinematic loop and four nonholonomic constraints and found that the resulting
symbolic linearized motion equations are identical to previously published
results.  The technique can be performed symbolically (enabling explict
analytical forms of the linearized dynamics) or numerically.
% Conclusion
Motion equations for constrained multibody systems can now be linearized in a
systematic fashion, symbolically or numerically, thereby facilitating common
linear analyses (e.g., stability analysis and control system design).
% Perspectives
Efficiency of computer implementations of this procedure will need to be
considered in future studies.
\keywords{symbolic dynamics, control, constrained multibody systems}
\end{abstract}

>>>>

\begin{abstract}
% Context
Many common mechanical systems have configuration or velocity constraints.
% Need  (what we have and what we want)
Analyses of such systems often require linearized forms of the motion
equations.  Although derivation of the nonlinear motion equations is well
understood, very little has been presented on the proper approach to
forming linearized versions which satisfy the constraints.
% Task
To address this issue, we developed a procedure for organizing the constraints
and motion equations, and subsequently linearizing these equations.
% Object of the document
In this paper we present this procedure to correctly linearize the nonlinear
motion equations of constrained multibody systems, and illustrate it with a
familiar example, the rolling disc.
% Findings
We apply this procedure to a model of a bicycle that includes a closed
kinematic loop and four nonholonomic constraints and find that the resulting
symbolic linearized motion equations are identical to previously published
results.  The technique can be performed symbolically (enabling explict
analytical forms of the linearized dynamics) or numerically.
% Conclusion
Motion equations for constrained multibody systems can now be linearized in a
systematic fashion, symbolically or numerically, thereby facilitating common
linear analyses (e.g., stability analysis and control system design).
% Perspectives
Efficiency of computer implementations of this procedure will be considered in
future studies.
\keywords{symbolic dynamics, control, constrained multibody systems}
\end{abstract}
